### 2014-11-13 tex/precise.tex

\section{Generating Summary Heaps}
\label{sec:precise}
In this section we present the summary heap algorithm that operates on
the bipartiate graph described in the previous section.  The summary
heap algorithm initializes, updates, and partitions the heap. It only
partitions the heap at points of divergence in the control flow graph
such as field accesses or writes (exeception control flow due to null
pointers) or comparisons of references (program control flow). There
are three sets of rewrite rules specific to the summary heap
algorithm: (i) rules to initialize symbolic references, (ii) rules to
complete field access and field write, and (iii) rules to check
equality and inequality of references. The other rules are common to
both $\rsym$ and $\rgse$. The complete set of rules are shown in the
supplemental attached with the paper.

@@

In~\figref{fig:symInit}, given the unitialized set $\Lambda$ for
field $f$, the $\mathit{min}_l$ function returns
$(\phi_x\ \cfgnt{l}_x)$ based on a lexicographical ordering of
uninitialized locations in $\Lambda$ to make initialization
deterministic (i.e., the same heap is always initialized in the same
way as order determines how many aliases are available in the input heap at any given point in initialization). 
%The $\mathrm{fresh}_\cfgnt{l}(\cfgnt{C})$ call returns a new location of type $C$. 
The set $\rho$ contains the set of
reference-location pairs from the input heap that are potential
aliases. Minimizing over the set of references in the pre-image ensures
that any pair in $\rho$ is the reference $\cfgnt{r}_a$ and the location $\cfgnt{l}_a$ materialized at the same time in some prior initialization (i.e., they were once
$\cfgnt{r}_f$ and $\cfgnt{l}_f$). Aliasing constraints
in the new summary heap reason over these original creators; otherwise aliasing and local value set
computation breaks down.  The reference partitions with their
monotonicity make this determination possible.

There are three sets corresponding to the non-deterministic choices in
GSE with a fourth that preserves the pre-initialized heap structure.
Note that the constraints always preserve the access path to the location which is $\phi_x$.
(i) $\theta_\mathit{null}$ asserts the condition under which
$\cfgnt{l}_\mathit{null}$ is possible (any time the solver assigns
values to reference variables in such a way that both $\phi_x$ and $\cfgnt{r}_f =
\cfgnt{r}_\mathit{null}$ hold). (ii)
$\theta_\mathit{new}$ is active when $\cfgnt{r}_f$ points to the
fresh location. This occurs when $\cfgnt{r}_f$ is not new or any other alias. (iii) each member of $\theta_\mathit{alias}$ restricts $\cfgnt{r}_f$ to
a particular alias in $\rho$, and at the same time, not alias any member of $\rho$
that was initialized earlier than the current choice (a later
initialization may indeed also alias the current choice in a valid
heap as order determines the number of aliasing choices available). And (iv) $\theta_\mathit{orig}$  implements conditional initialization to preserve the
original heap structure. This property is needed for the bisumulation. 
These sets are added into the heap on $\cfgnt{r}_f$ after the fields for $\cfgnt{l}_f$ are initialized to $\cfgnt{r}_\mathit{un}$.

>>>>

\section{Generating Summary Heaps}
\label{sec:precise}
In this section we present the summary heap algorithm that operates on
the bipartite graph described in the previous section.  The summary
heap algorithm initializes, updates, and partitions the heap. It only
partitions the heap at points of divergence in the control flow graph
such as field accesses or writes (execeptional control flow due to null
pointers) or comparisons of references (program control flow). There
are three sets of rewrite rules specific to the summary heap
algorithm: (i) rules to initialize symbolic references, (ii) rules to
complete field access and field write, and (iii) rules to check
equality and inequality of references. The other rules are common to
both $\rsym$ and $\rgse$. The complete set of rules are shown in the
supplemental attached with the paper.

@@

In~\figref{fig:symInit}, given the uninitialized set $\Lambda$ for
field $f$, the $\mathit{min}_l$ function returns
$(\phi_x\ \cfgnt{l}_x)$ based on a lexicographical ordering of
uninitialized locations in $\Lambda$ to make initialization
deterministic (i.e., the same heap is always initialized in the same
way as order determines how many aliases are available in the input heap at any given point in initialization). 
%The $\mathrm{fresh}_\cfgnt{l}(\cfgnt{C})$ call returns a new location of type $C$. 
The set $\rho$ contains the set of
reference-location pairs from the input heap that are potential
aliases. Minimizing over the set of references in the pre-image ensures
that any pair in $\rho$ is the reference $\cfgnt{r}_a$ and the location $\cfgnt{l}_a$ materialized at the same time in some prior initialization (i.e., they were once
$\cfgnt{r}_f$ and $\cfgnt{l}_f$). Aliasing constraints
in the new summary heap reason over these original creators; otherwise aliasing and local value set
computation breaks down.  The reference partitions with their
monotonicity make this determination possible.

There are three sets corresponding to the non-deterministic choices in
GSE with a fourth that preserves the pre-initialized heap structure.
Note that the constraints always preserve the access path to the location which is $\phi_x$.
(i) $\theta_\mathit{null}$ asserts the condition under which
$\cfgnt{l}_\mathit{null}$ is possible (any time the solver assigns
values to reference variables in such a way that both $\phi_x$ and $\cfgnt{r}_f =
\cfgnt{r}_\mathit{null}$ hold). (ii)
$\theta_\mathit{new}$ is active when $\cfgnt{r}_f$ points to the
fresh location. This occurs when $\cfgnt{r}_f$ is not new or any other alias. (iii) each member of $\theta_\mathit{alias}$ restricts $\cfgnt{r}_f$ to
a particular alias in $\rho$, and at the same time, not alias any member of $\rho$
that was initialized earlier than the current choice (a later
initialization may indeed also alias the current choice in a valid
heap as order determines the number of aliasing choices available). And (iv) $\theta_\mathit{orig}$  implements conditional initialization to preserve the
original heap structure. This property is needed for the bisimulation. 
These sets are added into the heap on $\cfgnt{r}_f$ after the fields for $\cfgnt{l}_f$ are initialized to $\cfgnt{r}_\mathit{un}$.
